---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# classifynewboRns

<!-- badges: start -->
[![R-CMD-check](https://github.com/simpar1471/classifynewboRns/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simpar1471/classifynewboRns/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Classify newborns with size for gestational age based on sex, age at birth in weeks, and birth weight

## Installation

You can install the development version of classifynewboRns from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("simpar1471/classifynewboRns")
library(classifynewboRns)
```

## Functionalities
### Built-in datasets
`classifynewboRns` comes with several in-built datasets for you to test its functions with. These include `bweight_centiles` (used to work out size for gestational age) and `bweight_data` (an example
data input).
```{r example_datasets1}
birthweight_centiles <- classifynewboRns::bweight_centiles
head(birthweight_centiles$male, 3); head(birthweight_centiles$female, 3); head(birthweight_centiles$unknown, 3)
```
```{r example_datasets2}
birthweight_data <- classifynewboRns::bweight_data
head(birthweight_data, 3)
```
### Calculating size for gestational age
Size for gestational age for newborns can be calculated using `annotate_bweight_table()` if the provided table has data on sex, age at birth and birth weight in kg:
```{r example_annotation}
birthweight_data_sga <- classifynewboRns::annotate_bweight_table(birthweight_data)
head(birthweight_data_sga, 3)

# Summary counts for observations of size for gestational age categories can be easily retrieved:
classifynewboRns::get_sfga_summaries(birthweight_data_sga$size_for_ga)
```
You can also calculate size for gestational age for one newborn:
```{r example_sga}
classifynewboRns::get_size_for_gestational_age(sex = "male", gestational.age.at.birth = 44, birthweight.in.kg = 3.42)
```
